---
title: "Multiple factors model using regression"
author: "UBSSDIC Quant Group"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Regression Method Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette aims to help you work with the regression method in multiple factors model. We will seperate the help file in following part:

- local regression tables
- regression result show
- portfolio optimization
- traditional portfolio construction

```{r setup,echo=FALSE,include=FALSE}
library(RFactorModel)
library(knitr)
knitr::opts_chunk$set(
  eval = FALSE,
  warning = FALSE
)
```


## local regression tables

Local database's factorlist table is as below.
```{r local_factorLists,eval=TRUE,echo=FALSE}
ftbale <- CT_FactorLists()
ftbale <- dplyr::arrange(ftbale,factorID)
kable(ftbale)
```


Get recommended factor lists by regression.
```{r getfactorlist}
# get recommended factorlists last year based on regression
begT <- Sys.Date()-months(6)
endT <- Sys.Date()-1
indexID <- 'EI000985'
re <- reg.factorlists_recommend(indexID,begT,endT)
FactorLists <- re$FactorLists
# recommend result
re$result
```


Show factors' correlation and statistic result.
```{r showfactorstat}
RebDates <- getRebDates(begT,endT)
TS <- getTS(RebDates,indexID)
TSF <- getMultiFactor(TS,FactorLists)
MF.chart.Fct_box(TSF)
MF.chart.Fct_corr(TSF)
MF.chart.Fct_density(TSF)

#remove strange factors
#FactorLists[[4]] <- NULL
#FactorLists[[1]] <- NULL
#FactorLists[[6]] <- NULL
#FactorLists[[8]] <- NULL
#TSF$F_ROE_1 <- NULL
#TSF$float_cap_ <- NULL
#TSF$disposition_ <- NULL
#TSF$ILLIQ <-NULL


```



Build and update local database's regression result tables.
```{r getlists_buildlocaltables}
# build local database's regression tables
system.time(lcdb.build.RegTables(FactorLists=FactorLists))

# update local database's regression tables
system.time(lcdb.update.RegTables(FactorLists = FactorLists))
```


## regression result show

```{r reg_result}
# parameter setting
begT <- trday.nearest(Sys.Date()-lubridate::years(3))
endT <- trday.nearest(Sys.Date()-30)
RebDates <- getRebDates(begT,endT)

# get TS,TSF,TSFR
TS <- getTS(RebDates,indexID)
TSF <- getMultiFactor(TS,FactorLists)
TSFR <- getTSR(TSF,date_end_pad = trday.nearest(Sys.Date()-1))
TSFR <- na.omit(TSFR)

# get regression result
reg_results <- reg.TSFR(TSFR)

## show regression result
# factor correlation plot
MC.chart.fCorr(TSF,Nbin='year')
# regression's rsquare plot
chart.reg.rsquare(reg_results)
# regression's rsquare table
table.reg.rsquare(reg_results)
# correlation plot of factor's return 
MC.chart.regCorr(reg_results)
# pure factor's wealth index
chart.reg.fRtnWealthIndex(reg_results,facet = T)
# barplot of pure factor's return 
chart.reg.fRtnBar(reg_results)
# summarise table of pure factor's return 
table.reg.fRtn(reg_results)
```


## portfolio optimization

```{r portOpt}
# set alpha factor
alphaf <- c("PB_mrq_","F_ROE_1","NP_YOY")

# get factor return
fRtn <- getfRtn(RebDates,alphaf,type = 'mean',reg_results = reg_results)
# get factor covariance
fCov <- getfCov(RebDates,alphaf,covtype='simple',reg_results = reg_results)



# Date Alignment
tmp.date1 <- max(min(fRtn$date),min(fCov$date))
tmp.date2 <- min(max(fRtn$date),max(fCov$date))
fRtn <- subset(fRtn,date>=tmp.date1,date<=tmp.date2)
fCov <- subset(fCov,date>=tmp.date1,date<=tmp.date2)
TSF <- subset(TSF,date>=tmp.date1,date<=tmp.date2)

## portfolio demo
# set factor's exposure
fexp <- buildFactorExp(PB_mrq_=c(-0.01,100),
                        volatility_ = c(-0.01, 0.01),
                        disposition_=c(-0.01,100),
                        beta_=c(-0.01, 0.01),
                        ln_mkt_cap_=c(-0.01,100),
                        NP_YOY=c(-0.01,100))
# simplest way:no benchmark,maximize return
system.time(port_opt <- OptWgt(TSF,alphaf,fRtn,fCov,target = 'return',factorExp = fexp))


#build weight setting
wgtSet <- buildWgtSet(ES33480000=c(0,0.05),ES33490000=c(0,0.03))

#build box constrain
boxConstr <- buildBoxConstr(EI000905=c(0.7,0.8))
# with benchmark,maximize return, box constrain
system.time(port_opt <- OptWgt(TSF,alphaf,fRtn,fCov,target = 'return',bmk = 'EI000985',factorExp = fexp,wgtSet = wgtSet))

# with benchmark,risk return balance
system.time(port_opt <- OptWgt(TSF,alphaf,fRtn,fCov,target = 'balance',bmk = 'EI000905',factorExp = fexp,boxConstr = boxConstr))



# port backtest and return summary
portrtn <- port.backtest(port_opt,fee.buy = 0.001)
benchrtn <- getrtn.bmk(portrtn, bmk = "EI000905")
allrtn <- addrtn.hedge(portrtn,benchrtn)
ggplot.WealthIndex(allrtn)
rtn.summary(allrtn)
rtn.periods(allrtn)
```


## traditional portfolio construction


```{r ICmethods}
#set modelPar
modelPar <- modelPar.default()
modelPar <- setmodelPar.time(modelPar,begT,endT)
modelPar <- setmodelPar.univ(modelPar,'EI000905')

#get factor wgt
factorIDs <- c("F000006","F000008","F000013","F000017")
tmp <- buildFactorLists_lcfs(factorIDs,factorStd="norm",factorNA = "mean")
FactorLists <- buildFactorLists(
  buildFactorList(factorFun="gf.NP_YOY",
                  factorPar=list(),
                  factorDir=1),
    buildFactorList(factorFun="gf.ln_mkt_cap",
                  factorPar=list(),
                  factorDir=1),
  factorStd="norm",factorNA = "median")
FactorLists <- c(tmp,FactorLists)
MPs <- getMPs_FactorLists(FactorLists, modelPar)
TSFRs <- Model.TSFRs(MPs)
wgt <- MC.wgt.CAPM(TSFRs,wgtmin = 0.05,wgtmax = 0.3)

#get port and backtest
TS <- Model.TS(modelPar)
TSF2 <- getMultiFactor(TS,FactorLists = FactorLists,wgts = wgt)
port2 <- getPort(TSF2,topN = 100,pick.sectorNe = T)
port2 <- port2[,c('date','stockID')]
port2 <- addwgt2port(port2, wgt.sectorNe = T, wgtbmk = "EI000905")
re2 <- port.backtest(port2,fee.buy = 0.001)
benchrtn2 <- getrtn.bmk(re2, bmk = "EI000905")
allrtn2 <- addrtn.hedge(re2,benchrtn2)
ggplot.WealthIndex(allrtn2)
rtn.summary(allrtn2)
rtn.periods(allrtn2)
```



